\co{Enhanced tunability in ferroelectric composites through local field enhancement and the effect of disorder}

### 2019-06-10 paper/arxiv/response_letter.tex

\item In the introduction: Local field engineering and field amplification has become more and more useful
 at other frequency ranges, especially in the THz and near-IR, to control the properties of other materials
  (eg. \href{https://doi.org/10.3390/photonics6010022}{Photonics 2019, 6(1), 22}). Could the authors expand
   on some other systems, besides ferro-electric metamaterials, that this method might apply to. For
    instance maybe tunable
    \href{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.110.217404}{GaAs meta-devices}.

\item In the introduction: The authors mention that there are generally limitations to the current
 numerical and theoretical models used in the field, but do not go into any detail. Could the authors
  expand on this point? What are the limitations?

\item Theory Section, A. In figure 1, are these electrostatics measurements performed by the authors? It is
 unclear based on the figure and surrounding paragraphs. I assume they are as no citation is provided for
  the data. Could the authors discuss the details of how these measurements were made? This would be useful
   for metamaterials researchers who do not work in this frequency range.

\rep{Details about the composition, fabrication and measurements of the samples at DC and microwaves have been added at the beginning of Theory Section, A.}

@@

\item Theory: Equation 3 is normally referred to as Gauss' Law (or it is at least Gauss' Law written in
 terms of V).

 \rep{Reference to Gauss' law has been added before Eq. 3}

\item Figure 3 c) It is unclear what is being plotted here. Is this the tunability, n, defined at the
 beginning of the introduction? If so, please label using previously defined notation.

 \rep{The captions of Figure 3 and other plots have been updated with more details (we are plotting normalized values),
 and more precisions have been added in the main text (section III. A)}

### 2019-06-10 paper/arxiv/marked_manuscript.tex
poster and corrections

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}

@@

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
 We investigate \co{numerically} the homogenized permittivities of metamaterials made of low index dielectric inclusions in a feroelectric matrix under
 a static electric field. A refined model is used to take into account the coupling
 between the electrostatic problem and the electric field dependent permittivity of the
 ferroelectric material, leading to a local field enhancement and permittivity change in the ferroelectric.
 Periodic and pseudo-random structures in two dimensions are investigated and
 we \co{compute} the effective permittivity, losses, electrically induced anisotropy and tunability
 of those metamaterials. We show that the tunability of such composites might be substantially
 enhanced in the periodic case, wherehas introducing disorder in the microstructure
 weaken the effect of enhanced local permittivity change. Our results may be useful to guide the synthesis of novel composite ceramics with improved characteristics for controllable microwave devices.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

 applications. Thus it has been considered to mix ferroelectric ceramics to low-index and

@@

medium approach for low concentration of dielectrics were derived for diferent configurations (columnar, layered and spherical
inclusions models) and have succesfully be compared with numerical simulations and experiments \cite{sherman_ferroelectric-dielectric_2006}.

@@

the grain boundaries, and the predicted behavior succesfully compared to experimental data \cite{padurariu_field-dependent_2012}.

@@

litterature \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012}, we account for

@@

\co{The model we developped has been implemented with the finite element method (FEM)

@@

First, we consider} metamaterials consisting of a squarre array of parallel

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=1\columnwidth]{epsilon_fit}
 \caption{Variation of the ferroelectric permittivity as a function of the
  applied electric field (dots: measurements, dashed lines: fit to
  formula~(\ref{eq_epsf})), for the static case (green) and at microwave frequencies
  (orange, $f=3.8$ GHz). The fitting parameters are given in Table \ref{table_params_fit}.}
 \label{fig1}
\end{figure}
We use barium strontium titanate (BST) as our ferroelectric material. Measurements
have been carried out at electrostatics and at microwave frequencies, and the normalized permittivity value
as a function of biasing field are reported on \fig{fig1}.\\
To describe the permittivity, we make use of the Landau potential
given by $F(P,E) = F_0 +  a P^2/2 + b P^4/4 + cP^6/6 - EP$, where $E$ is
the applied electric field and $P$ is the polarization \cite{landau_electrodynamics_2013, zhou_dielectric_2008}. Variations of the
permittivity with the temperature can be taken into account through the
coefficients $a$, $b$ and $c$, but we assume we are working at a constant
room temperature. We further assume that the material is not subject to any stress, so that the variation
of permittivity due to mechanical constraints is irrelevant.
The equation of state $$\frac{\partial F (P, E)}{\partial P}   = a P_0 + b P_0^3 + c P_0^5 - E = 0$$ gives the
dependence of the polarization on the applied electric field,
with $P_0$ being the equilibrium polarization.
Along the direction of a uniform applied electric field, the relative permittivity is given by:
\begin{equation}
 \epsf(E) = \left[\frac{\partial^2 F (P, E)}{\partial P^2} \right]^{-1} = \frac{\epsf(0)}{1 + \alpha P_0^2 + \beta P_0^4},
 \label{eq_epsf}
\end{equation}
where $\epsf(0)=1/a$, $\alpha=3b/a$ and $\beta=5c/a$. The fitting parameters are given in Table \ref{table_params_fit}.
As the norm of the field increases, the permittivity decreases with a characteristic
bell curve typical for a ferroelectric material in its paraelectric state.
Furthermore, assuming the crystalline principal axes of the ferroelectric material
are oriented in the coordinate directions, and that the diagonal components of the permittivity
tensor are only function of the corresponding bias electric field components \cite{krowne_anisotropic_2002}, we have:
\begin{equation}
 \epsftens (\B E) =
 \left(
 \begin{matrix}
   \epsf_{xx}(E_x) & 0               & 0 \cr
   0               & \epsf_{yy}(E_y) & 0 \cr
   0               & 0               & \epsf_{zz}(E_z) \cr

  \end{matrix}
 \right)
 \label{eq_epsftens}
\end{equation}
where each of the diagonal components have the functional form
given by \equ{eq_epsf}. Note that we will use the static values of permittivity
for the electrostatic modelling, while we are interrested in the homogenized values
of permittivity at microwaves.\\
\begin{table}
 \caption{Fitting parameters to model (\ref{eq_epsf}) for the measured permittivity values as a function
  of applied electrc field shown on \fig{fig1}. }
 \label{table_params_fit}
 \begin{tabular}{llll}
  \hline
  case        & $\epsf(0)$ & $\alpha$ ($\rm \mu m^2/V^2$) & $\beta$ ($\rm \mu m^4/V^4$) \\ \hline
  static      & 3050       & 0.120                        & 0.024                       \\
  $f=3.8$ GHz & 165        & 0.240                        & 0.079                       \\\hline
 \end{tabular}
\end{table}

\begin{figure*}[!t]
 \centering
 \includegraphics[width=0.75\textwidth]{convergence_per}
 \caption{Convergence of the coupled problem.
  Real part (a) and loss tangent (b) of the components of the homogenized
  permittivity tensor as a function of iteration step $i$. The distribution of
  the normalized electric field (colour map: magnitude in logarithmic scale,
  lines: equipotential contours) and of the
  $xx$ component of the permittivity tensor are shown for $i=1$
  (c and d) and $i=12$ (e and f).
 }
 \label{conv2D}
\end{figure*}

% -------------------------------------------------------------------------------
\subsection{Electrostatic model}
The composites under study are made of two materials, thus their permittivity
is represented by a piecewise defined tensor $\epstens(\B r, \B E)$ which is
equal to $\epsftens(\B E(\B r))$ in the ferroelectric phase and ${\rm diag}(\epsd)$
in the dielectric phase.
In the following, we consider two different cases for the biasing field.
Because of the form~(\ref{eq_epsftens}) assumed for the ferroelectric permittivity
tensor, $\varepsilon_{zz}$ will not be changing for a field in the plane orthogonal
to the $z$ axis. This is the only component
being relevant for TE polarization, so we consider in this case a uniform biasing
electric field applied along the direction of invariance $\B E_0 = E_{0} \B e_z$.
On the other hand,
the in-plane components of $\epsftens$ are tuned by $E_x$ and $E_y$, therefore,
without loss of generality,
we consider a uniform applied electric field directed along the $x$ axis
$\B E_0 = E_{0} \B e_x$ for the TM polarization case.
To calculate the total electric field in the material, one
has to solve the electrostatic equation for the potential $V$:
\begin{equation}
 \div (\epstens \grad V) = 0
 \label{eq_elstat}
\end{equation}
Note that for the TE case, the solution is trivial since the structures
are invariant along $z$, so that the electric field is equal to the uniform biasing field, and
we will thus not study it in the following.
However in the TM case, the situation is much more complex: this is a coupled problem since the
electric field $\B E=-\grad V$ derived from the
solution of \equ{eq_elstat} depends on the permittivity distribution, which
itself depends on the electric field.
The coupled system formed
of Eqs.~(\ref{eq_epsftens}) and (\ref{eq_elstat}) is solved iteratively until there
is convergence on the norm of the electric field.
Here we would like to emphasise that the permittivity in the ferroelectric material, although
uniform initially, is spatially varying due to the non-uniform distribution
of the total electric field.\\

% -------------------------------------------------------------------------------
\subsection{Homogenization}
The effective permittivity for TM polarization is calculated
using two scale homogenization technique \cite{allaire_homogenization_1992, guenneau_homogenization_2000}.
For this purpose, one has to find the solutions
$\psi_j$ of two annex problems $\mathcal P_j$, $j=\{1, 2\}$:
\begin{equation}
 \div \left[ \xitens \grad(\psi_j + r_j) \right] = 0,
 \label{eq_hom_annex}
\end{equation}
where $\B r = (x, y)^{\rm T}$ is the position vector in the $xy$ plane and
$\xitens=\epstens^{\rm T}/ {\rm det }(\epstens)$.
The homogenized tensor $\xihom$ is obtained with:
\begin{equation}
 \xihom = \langle \xitens \rangle + \B \phi,
 \label{eq_hom}
\end{equation}
where $\langle . \rangle$ denotes the mean value over the unit cell.
The elements of the matrix $\B \phi$ represent correction terms and
are given by $\B \phi_{ij} = \langle \xitens \grad \psi_i \rangle_j$.
Finally the effective permittivity tensor can be calculated using $\epshom=\xihom^{\rm T}/ {\rm det }(\xihom)$.\\
Note that the TE case, which we shall not study here as no coupling happens, is trivial since
the homogenized permittivity is simply the average of the permittivity in the unit cell:
$\epshom = \langle \epstens \rangle$.

@@

\begin{figure*}[!t]
 \centering
 \includegraphics[width=0.75\textwidth]{effective_params_per}
 \caption{Effective parameters of the 2D metamaterials as a function of the
  applied electric field for various filling fraction of dielectric.
  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
  (d): anisotropy factor. The solid lines correspond to the coupled model and
  the dashed lines to the uncoupled model.}
 \label{eff_par_2D_TM}
\end{figure*}

@@

\begin{figure*}[!t]
 \centering
 \includegraphics[width=0.75\textwidth]{effpar_rand_cpl.png}
 \caption{Effective parameters of the pseudo-random composites as a function of the
  applied electric field for various filling fraction of dielectric, when the
  coupling is taken into account.
  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
  (d): anisotropy factor. The solid lines represent the average values
  over the 21 samples and the lighter error bands show a confidence interval corresponding to
  the standard deviation.}
 \label{eff_par_2Drand_TM}
\end{figure*}
%
%
%

@@

Lets us now consider a periodc square array of infinitely long dielectric rods of circular cross section

@@

 of bulk ferroelectric. Two concurrent effects are at stake here: on the one hand

@@

 in our coupled model compared to the uncoupled one (cf. Fig.~(\ref{eff_par_2D_TM}.d)).

@@

  permittivity tensor as a function of iteration step $i$. The distribution of

@@

\begin{figure*}[h!]
 \centering
 \includegraphics[width=0.8\textwidth]{effpar_rand_uncpl.png}
 \caption{Effective parameters of the random 2D mixtures as a function of the
  applied electric field for various filling fraction of dielectric, when the
  coupling is neglected.
  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
  (d): anisotropy factor. The solid lines represent the average values
  over the 21 samples and the lighter error bands show a confidence interval corresponding to
  the standard deviation.}
 \label{eff_par_2Drand_TM_uncpl}
\end{figure*}
%
\section{Conclusion}

We have studied the homogenized properties of dielectric/ferroelectric mixtures
using a rigorous model that take into account the coupling between the electrostatic
field distribution and the field dependant ferroelectric permittivity tensor. After
convergence of the coupled problem, the effective permittivity tensor is calculated using
two scale convergence homogenization theory.
The results obtained by this model differ significantly from a simple assumption that
the permittivity of the ferroelectric respond just to the uniform biasing field.
We have considered both periodic and random arrays
of dielectric rods in a ferroelectric matrix in 2D, and studied their effective properties
for TM polarization as a function of dielectric concentration and bias field.
Importantly, adding more low index and low loss dielectric allows to decrease
the overall permittivity significantly and slightly lower the losses.
For the periodic case, the tunability is higher than the bulk due to local field enhancement, whereas
this effect is strongly suppressed when disorder is introduced. The assymetric redistribution of the permittivity
induce an effective anisotropy that is added to the one arising purely from the ferroelectric material.
The properties of the composites are affected by multiple factors:
geometry and the spatially dependent electric field that will induce locally a tunable, anisotropic
response in the ferroelectric phase depending on its amplitude and direction.
This suggest that the performances of the composites
may be enhanced by distributing the two phases in an optimal way to get high
tunability and low losses. Further work in that direction is needed as well as
extending this study to 3D media.
Finally, because the permittivity of the dielectric is much smaller than the ferroelectric one,
it would be of great interest to use high contrast homogenization theory
\cite{bouchitte_homogenization_2004, cherednichenko_homogenization_2015} to
study this kind of mixtures.
This would reveal the frequency dependant artificial magnetism due to "micro-resonances"
in the high index phase and potentially lead to composites with tunable effective permeability.

@@

\vskip2pc

\begin{thebibliography}{99}

\bibitem{tagantsev_ferroelectric_2018}
Tagantsev AK, Sherman VO, Astafiev KF, Venkatesh J, Setter N. 2018
  Ferroelectric {Materials} for {Microwave} {Tunable} {Applications}. {\em J.
  Electroceram.} \textbf{11}, 5--66.

\bibitem{vendik_ferroelectric_1999}
Vendik O, Hollmann E, Kozyrev A, Prudan A. 1999  Ferroelectric tuning of planar
  and bulk microwave devices. {\em Journal of Superconductivity} \textbf{12},
  325--338.

\bibitem{lancaster_thin-film_1998}
Lancaster M, Powell J, Porch A. 1998  Thin-film ferroelectric microwave
  devices. {\em Superconductor Science and Technology} \textbf{11}, 1323.

\bibitem{xi_oxide_2000}
Xi X, Li HC, Si W, Sirenko A, Akimov I, Fox J, Clark A, Hao J. 2000  Oxide thin
  films for tunable microwave devices. {\em Journal of Electroceramics}
  \textbf{4}, 393--405.

\bibitem{hand_frequency_2008}
Hand TH, Cummer SA. 2008  Frequency tunable electromagnetic metamaterial using
  ferroelectric loaded split rings. {\em Journal of Applied Physics}
  \textbf{103}, 066105.

\bibitem{zhao_experimental_2008}
Zhao H, Kang L, Zhou J, Zhao Q, Li L, Peng L, Bai Y. 2008  Experimental
  demonstration of tunable negative phase velocity and negative refraction in a
  ferromagnetic/ferroelectric composite metamaterial. {\em Applied Physics
  Letters} \textbf{93}, 201106.

\bibitem{sherman_ferroelectric-dielectric_2006}
Sherman VO, Tagantsev AK, Setter N, Iddles D, Price T. 2006
  Ferroelectric-dielectric tunable composites. {\em Journal of Applied Physics}
  \textbf{99}, 074104.

\bibitem{jylha_tunability_2008}
Jylha L, Sihvola AH. 2008  Tunability of granular ferroelectric dielectric
  composites. {\em Progress in Electromagnetics Research} \textbf{78},
  189--207.

\bibitem{sherman_tunability_2004}
Sherman VO, Tagantsev AK, Setter N. 2004  Tunability and loss of the
  ferroelectric-dielectric composites. In {\em 14th {IEEE} {International}
  {Symposium} on {Applications} of {Ferroelectrics}, 2004. {ISAF}-04. 2004} pp.
  33--38.

\bibitem{astafiev_can_2003}
Astafiev KF, Sherman VO, Tagantsev AK, Setter N. 2003  Can the addition of a
  dielectric improve the figure of merit of a tunable material?. {\em Journal
  of the European Ceramic Society} \textbf{23}, 2381 -- 2386.

\bibitem{okazaki_effects_1973}
Okazaki K, Nagata K. 1973  Effects of {Grain} {Size} and {Porosity} on
  {Electrical} and {Optical} {Properties} of {PLZT} {Ceramics}. {\em Journal of
  the American Ceramic Society} \textbf{56}, 82--86.

\bibitem{stanculescu_study_2015}
Stanculescu R, Ciomaga CE, Padurariu L, Galizia P, Horchidan N, Capiani C,
  Galassi C, Mitoseriu L. 2015  Study of the role of porosity on the functional
  properties of ({Ba},{Sr}){TiO}3 ceramics. {\em Journal of Alloys and
  Compounds} \textbf{643}, 79--87.

\bibitem{padurariu_tailoring_2012}
Padurariu L, Curecheriu L, Galassi C, Mitoseriu L. 2012a  Tailoring non-linear
  dielectric properties by local field engineering in anisotropic porous
  ferroelectric structures. {\em Appl. Phys. Lett.} \textbf{100}, 252905.

\bibitem{padurariu_field-dependent_2012}
Padurariu L, Curecheriu L, Buscaglia V, Mitoseriu L. 2012b  Field-dependent
  permittivity in nanostructured {BaTiO}$_3$ ceramics: {Modeling} and
  experimental verification. {\em Phys. Rev. B} \textbf{85}, 224111.

\bibitem{cazacu_tunable_2013}
Cazacu A, Curecheriu L, Neagu A, Padurariu L, Cernescu A, Lisiecki I, Mitoseriu
  L. 2013  Tunable gold-chitosan nanocomposites by local field engineering.
  {\em Appl. Phys. Lett.} \textbf{102}, 222903.

\bibitem{allaire_homogenization_1992}
Allaire G. 1992  Homogenization and {Two}-{Scale} {Convergence}. {\em SIAM
  Journal on Mathematical Analysis} \textbf{23}, 1482--1518.

\bibitem{guenneau_homogenization_2000}
Guenneau S, Zolla F. 2000  Homogenization of {Three}-{Dimensional} {Finite}
  {Photonic} {Crystals}. {\em Journal of Electromagnetic Waves and
  Applications} \textbf{14}, 529--530.

\bibitem{landau_electrodynamics_2013}
Landau LD, Bell J, Kearsley M, Pitaevskii L, Lifshitz E, Sykes J. 2013 {\em
  Electrodynamics of continuous media} vol.~8.
elsevier.

\bibitem{zhou_dielectric_2008}
Zhou K, Boggs SA, Ramprasad R, Aindow M, Erkey C, Alpay SP. 2008  Dielectric
  response and tunability of a dielectric-paraelectric composite. {\em Applied
  Physics Letters} \textbf{93}, 102908.

\bibitem{krowne_anisotropic_2002}
Krowne CM, Daniel M, Kirchoefer SW, Pond JA. 2002  Anisotropic permittivity and
  attenuation extraction from propagation constant measurements using an
  anisotropic full-wave {Green}'s function solver for coplanar ferroelectric
  thin-film devices. {\em IEEE Transactions on Microwave Theory and Techniques}
  \textbf{50}, 537--548.

\bibitem{geuzaine_gmsh:_2009}
Geuzaine C, Remacle JF. 2009  Gmsh: {A} 3-{D} finite element mesh generator
  with built-in pre- and post-processing facilities. {\em International Journal
  for Numerical Methods in Engineering} \textbf{79}, 1309--1331.

\bibitem{dular_general_1998}
Dular P, Geuzaine C, Henrotte F, Legros W. 1998  A general environment for the
  treatment of discrete problems and its application to the finite element
  method. {\em IEEE Transactions on Magnetics} \textbf{34}, 3395--3398.

\bibitem{amestoy_fully_2001}
Amestoy PR, Duff IS, Koster J, L'Excellent JY. 2001  A {Fully} {Asynchronous}
  {Multifrontal} {Solver} {Using} {Distributed} {Dynamic} {Scheduling}. {\em
  SIAM Journal on Matrix Analysis and Applications} \textbf{23}, 15--41.

\bibitem{bouchitte_homogenization_2004}
Bouchitté G, Felbacq D. 2004  Homogenization near resonances and artificial
  magnetism from dielectrics. {\em Comptes Rendus Mathématique} \textbf{339},
  377 -- 382.

\bibitem{cherednichenko_homogenization_2015}
Cherednichenko K, Cooper S. 2015  Homogenization of the system of high-contrast
  {Maxwell} equations. {\em Mathematika} \textbf{61}, 475--500.

\end{thebibliography}

% \bibliographystyle{RS}
% \bibliography{biblio}

>>>>

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}

@@

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
 We investigate \co{numerically} the homogenized permittivities of metamaterials made of low index dielectric inclusions in a ferroelectric matrix under
 a static electric field. A refined model is used to take into account the coupling
 between the electrostatic problem and the electric field dependent permittivity of the
 ferroelectric material, leading to a local field enhancement and permittivity change in the ferroelectric.
 Periodic and pseudo-random structures in two dimensions are investigated and
 we \co{compute} the effective permittivity, losses, electrically induced anisotropy and tunability
 of those metamaterials. We show that the tunability of such composites might be substantially
 enhanced in the periodic case, \co{whereas} introducing disorder in the microstructure
 weaken the effect of enhanced local permittivity change. Our results may be useful to guide the synthesis of novel composite ceramics with improved characteristics for controllable microwave devices.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

 applications. Thus it has been considered to mix ferroelectric \co{ceramics with} low-index and

@@

medium approach for low concentration of dielectrics were derived for different configurations (columnar, layered and spherical
inclusions models) and have been successfully compared with numerical simulations and experiments \cite{sherman_ferroelectric-dielectric_2006}.

@@

the grain boundaries, and the predicted behaviour successfully compared to experimental data \cite{padurariu_field-dependent_2012}.

@@

\co{literature} \cite{padurariu_tailoring_2012,padurariu_field-dependent_2012}, we account for

@@

\co{The model we developed has been implemented with the finite element method (FEM)

@@

First, we consider} metamaterials consisting of a square array of parallel

@@

\begin{figure}[!t]
 \centering
 \includegraphics[width=1\columnwidth]{epsilon_fit}
 \caption{Variation of the ferroelectric permittivity as a function of the
  applied electric field (dots: measurements, dashed lines: fit to
  formula~(\ref{eq_epsf})), for the static case (green) and at microwave frequencies
  (orange, $f=3.8$ GHz). The fitting parameters are given in Table \ref{table_params_fit}.}
 \label{fig1}
\end{figure}
We use barium strontium titanate (BST) as our ferroelectric material.
\co{
${\rm Ba}_{x}{\rm Sr}_{1-x}{\rm TiO}_3$ samples were fabricated using the conventional sintering method with a barium ratio of $x = 0.6$ to obtain a dielectrically tunable material as reported in the literature \cite{agrawal_tunable_2004, hu_preparation_2015}. The tunability was measured using an impedance analyzer up to 100 MHz, and at 3.8 GHz using a loaded microstrip split ring resonator \cite{ansari_design_2015}. The measured tunability of the in-house BST samples of 27\% under 1kv/mm DC bias was in agreement with those reported elsewhere \cite{agrawal_tunable_2004, hu_preparation_2015}. The method presented is however general and only relies of the gradient of the dielectric tunability vs electric field and could be applied to any tunable host material.
The normalized permittivity value
as a function of biasing field are reported on \fig{fig1}.\\}
To describe the permittivity, we make use of the Landau potential
given by $F(P,E) = F_0 +  a P^2/2 + b P^4/4 + cP^6/6 - EP$, where $E$ is
the applied electric field and $P$ is the polarization \cite{landau_electrodynamics_2013, zhou_dielectric_2008}. Variations of the
permittivity with the temperature can be taken into account through the
coefficients $a$, $b$ and $c$, but we assume we are working at a constant
room temperature. We further assume that the material is not subject to any stress, so that the variation
of permittivity due to mechanical constraints is irrelevant.
The equation of state $$\frac{\partial F (P, E)}{\partial P}   = a P_0 + b P_0^3 + c P_0^5 - E = 0$$ gives the
dependence of the polarization on the applied electric field,
with $P_0$ being the equilibrium polarization.
Along the direction of a uniform applied electric field, the relative permittivity is given by:
\begin{equation}
 \epsf(E) = \left[\frac{\partial^2 F (P, E)}{\partial P^2} \right]^{-1} = \frac{\epsf(0)}{1 + \alpha P_0^2 + \beta P_0^4},
 \label{eq_epsf}
\end{equation}
where $\epsf(0)=1/a$, $\alpha=3b/a$ and $\beta=5c/a$. The fitting parameters are given in Table \ref{table_params_fit}.
As the norm of the field increases, the permittivity decreases with a characteristic
bell curve typical for a ferroelectric material in its paraelectric state.
Furthermore, assuming the crystalline principal axes of the ferroelectric material
are oriented in the coordinate directions, and that the diagonal components of the permittivity
tensor are only function of the corresponding bias electric field components \cite{krowne_anisotropic_2002}, we have:
\begin{equation}
 \epsftens (\B E) =
 \left(
 \begin{matrix}
   \epsf_{xx}(E_x) & 0               & 0 \cr
   0               & \epsf_{yy}(E_y) & 0 \cr
   0               & 0               & \epsf_{zz}(E_z) \cr

  \end{matrix}
 \right)
 \label{eq_epsftens}
\end{equation}
where each of the diagonal components have the functional form
given by \equ{eq_epsf}. Note that we will use the static values of permittivity
for the electrostatic modelling, while we are \co{interested} in the homogenized values
of permittivity at microwaves.\\
\begin{table}
 \caption{Fitting parameters to model (\ref{eq_epsf}) for the measured permittivity values as a function
  of applied electric field shown on \fig{fig1}. }
 \label{table_params_fit}
 \begin{tabular}{llll}
  \hline
  case        & $\epsf(0)$ & $\alpha$ ($\rm \mu m^2/V^2$) & $\beta$ ($\rm \mu m^4/V^4$) \\ \hline
  static      & 3050       & 0.120                        & 0.024                       \\
  $f=3.8$ GHz & 165        & 0.240                        & 0.079                       \\\hline
 \end{tabular}
\end{table}

\begin{figure*}[!t]
 \centering
 \includegraphics[width=0.75\textwidth]{convergence_per}
 \caption{Convergence of the coupled problem.
  Real part (a) and loss tangent (b) of the components of the homogenized
  permittivity tensor as a function of iteration step $i$. \co{The values are normalized to the corresponding quantities for the bulk ferroelectric material.} The distribution of
  the normalized electric field (colour map: magnitude in logarithmic scale,
  lines: equipotential contours) and of the
  $xx$ component of the permittivity tensor are shown for $i=1$
  (c and d) and $i=12$ (e and f).
 }
 \label{conv2D}
\end{figure*}

% -------------------------------------------------------------------------------
\subsection{Electrostatic model}
The composites under study are made of two materials, thus their permittivity
is represented by a piecewise defined tensor $\epstens(\B r, \B E)$ which is
equal to $\epsftens(\B E(\B r))$ in the ferroelectric phase and ${\rm diag}(\epsd)$
in the dielectric phase.
In the following, we consider two different cases for the biasing field.
Because of the form~(\ref{eq_epsftens}) assumed for the ferroelectric permittivity
tensor, $\varepsilon_{zz}$ will not be changing for a field in the plane orthogonal
to the $z$ axis. This is the only component
being relevant for TE polarization, so we consider in this case a uniform biasing
electric field applied along the direction of invariance $\B E_0 = E_{0} \B e_z$.
On the other hand,
the in-plane components of $\epsftens$ are tuned by $E_x$ and $E_y$, therefore,
without loss of generality,
we consider a uniform applied electric field directed along the $x$ axis
$\B E_0 = E_{0} \B e_x$ for the TM polarization case.
To calculate the total electric field in the material, \co{one
has to solve for the potential $V$ satisfying Gauss' law:}
\begin{equation}
 \div (\epstens \grad V) = 0
 \label{eq_elstat}
\end{equation}
Note that for the TE case, the solution is trivial since the structures
are invariant along $z$, so that the electric field is equal to the uniform biasing field, and
we will thus not study it in the following.
However in the TM case, the situation is much more complex: this is a coupled problem since the
electric field $\B E=-\grad V$ derived from the
solution of \equ{eq_elstat} depends on the permittivity distribution, which
itself depends on the electric field.
The coupled system formed
of Eqs.~(\ref{eq_epsftens}) and (\ref{eq_elstat}) is solved iteratively until there
is convergence on the norm of the electric field.
Here we would like to emphasise that the permittivity in the ferroelectric material, although
uniform initially, is spatially varying due to the non-uniform distribution
of the total electric field.\\

% -------------------------------------------------------------------------------
\subsection{Homogenization}
\co{When the period of the composite metamaterial is much smaller than the wavelength, one can
describe the properties of the composite by a bulk medium with homogenized parameters.}
The effective permittivity for TM polarization is calculated
using a two scale convergence homogenization technique \cite{allaire_homogenization_1992, guenneau_homogenization_2000}.
For this purpose, one has to find the solutions
$\psi_j$ of two annex problems $\mathcal P_j$, $j=\{1, 2\}$:
\begin{equation}
 \div \left[ \xitens \grad(\psi_j + r_j) \right] = 0,
 \label{eq_hom_annex}
\end{equation}
where $\B r = (x, y)^{\rm T}$ is the position vector in the $xy$ plane and
$\xitens=\epstens^{\rm T}/ {\rm det }(\epstens)$.
The homogenized tensor $\xihom$ is obtained with:
\begin{equation}
 \xihom = \langle \xitens \rangle + \B \phi,
 \label{eq_hom}
\end{equation}
where $\langle . \rangle$ denotes the mean value over the unit cell.
The elements of the matrix $\B \phi$ represent correction terms and
are given by $\B \phi_{ij} = \langle \xitens \grad \psi_i \rangle_j$.
Finally the effective permittivity tensor can be calculated using $\epshom=\xihom^{\rm T}/ {\rm det }(\xihom)$.\\
Note that the TE case, which we shall not study here as no coupling happens, is trivial since
the homogenized permittivity is simply the average of the permittivity in the unit cell:
$\epshom = \langle \epstens \rangle$.

@@

\begin{figure*}[!t]
 \centering
 \includegraphics[width=0.75\textwidth]{effective_params_per}
 \caption{Effective parameters of the 2D metamaterials as a function of the
  applied electric field for various filling fraction of dielectric.
  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
  (d): anisotropy factor. The solid lines correspond to the coupled model and
  the dashed lines to the uncoupled model. \co{The values are normalized to the corresponding quantities for the bulk ferroelectric material.}}
 \label{eff_par_2D_TM}
\end{figure*}

@@

\begin{figure*}[!t]
 \centering
 \includegraphics[width=0.75\textwidth]{effpar_rand_cpl.png}
 \caption{Effective parameters of the pseudo-random composites as a function of the
  applied electric field for various filling fraction of dielectric, when the
  coupling is taken into account.
  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
  (d): anisotropy factor. The solid lines represent the average values
  over the 21 samples and the lighter error bands show a confidence interval corresponding to
  the standard deviation. \co{The values are normalized to the corresponding quantities for the bulk ferroelectric material.}}
 \label{eff_par_2Drand_TM}
\end{figure*}
%

@@

Lets us now consider a periodic square array of infinitely long dielectric rods of circular cross section

@@

 of bulk ferroelectric. \co{This can be seen in \fig{eff_par_2D_TM}.c where we plot the tunability of the composites
 along the $x$ axis, $\tilde{n}(E) = \tilde{\varepsilon_{xx}}(E) / \tilde{\varepsilon_{xx}}(0)$, normalized to the tunability of the bulk ferroelectric $n(E) = \epsf_{xx}(E) / \epsf_{xx}(0)$.}
 Two concurrent effects are at stake here: on the one hand

@@

 in our coupled model compared to the uncoupled one (cf. Fig.~(\ref{eff_par_2D_TM}.d) \co{where we plot the anisotropy factor \co{$\alpha =\varepsilon_{xx} / \varepsilon_{yy}$}}).

@@

  permittivity tensor as a function of iteration step $i$ \co{The values are normalized to the corresponding quantities for the bulk ferroelectric material.}. The distribution of

@@

\begin{figure*}[h!]
 \centering
 \includegraphics[width=0.8\textwidth]{effpar_rand_uncpl.png}
 \caption{Effective parameters of the random 2D mixtures as a function of the
  applied electric field for various filling fraction of dielectric, when the
  coupling is neglected.
  (a): normalized permittivity, (b): normalized loss tangent, (c): normalized tunability and
  (d): anisotropy factor. The solid lines represent the average values
  over the 21 samples and the lighter error bands show a confidence interval corresponding to
  the standard deviation. \co{The values are normalized to the corresponding quantities for the bulk ferroelectric material.}}
 \label{eff_par_2Drand_TM_uncpl}
\end{figure*}
%
\section{Conclusion}

We have studied the homogenized properties of dielectric/ferroelectric mixtures
using a rigorous model that take into account the coupling between the electrostatic
field distribution and the field dependant ferroelectric permittivity tensor. After
convergence of the coupled problem, the effective permittivity tensor is calculated using
two scale convergence homogenization theory.
The results obtained by this model differ significantly from a simple assumption that
the permittivity of the ferroelectric respond just to the uniform biasing field.
We have considered both periodic and random arrays
of dielectric rods in a ferroelectric matrix in 2D, and studied their effective properties
for TM polarization as a function of dielectric concentration and bias field.
Importantly, adding more low index and low loss dielectric allows to decrease
the overall permittivity significantly and slightly lower the losses.
For the periodic case, the tunability is higher than the bulk due to local field enhancement, whereas
this effect is strongly suppressed when disorder is introduced. The asymmetric redistribution of the permittivity
induce an effective anisotropy that is added to the one arising purely from the ferroelectric material.
The properties of the composites are affected by multiple factors:
geometry and the spatially dependent electric field that will induce locally a tunable, anisotropic
response in the ferroelectric phase depending on its amplitude and direction.
This suggest that the performances of the composites
may be enhanced by distributing the two phases in an optimal way to get high
tunability and low losses. Further work in that direction is needed as well as
extending this study to 3D media.
Finally, because the permittivity of the dielectric is much smaller than the ferroelectric one,
it would be of great interest to use high contrast homogenization theory
\cite{bouchitte_homogenization_2004, cherednichenko_homogenization_2015} to
study this kind of mixtures.
This would reveal the frequency dependant artificial magnetism due to "micro-resonances"
in the high index phase and potentially lead to composites with tunable effective permeability.\\
To finish, the general method followed by this model could be applied to other type of tunable
systems including for example ferromagnetic materials, liquid crystals, or
 field-enhanced carrier dynamics in doped semiconductors
\cite{keiser_terahertz_2019}
\cite{fan_nonlinear_2013}

@@

% \bibliographystyle{RS}
\bibliography{../biblio}
